---
title: "crisprVerse: ecosystem of R packages for CRISPR gRNA design"
output: 
  github_document:
    toc: true
---

```{r, echo=FALSE, results="hide"}
options("knitr.graphics.auto_pdf"=TRUE)
```

Authors: Jean-Philippe Fortin, Luke Hoberecht

Date: July 25, 2022



# Installation and getting started

The crisprVerse is a collection of packages for CRISPR guide RNA (gRNA) design
that can easily be installed with a single package, which is called
`crisprVerse". This provides a convenient way of downloading and installing all crisprVerse packages with a single R command:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("Jfortin1/crisprVerse")
```

The core crisprVerse includes the packages that are commonly used for gRNA design, adn are attached when you attach the `crisprVerse` package:

```{r}
library(crisprVerse)
```


# Components

The following packages are installed and loaded with the `crisprVerse` package: 


* [crisprBase](https://github.com/Jfortin1/crisprBase) to specify and manipulate CRISPR nucleases.
* [crisprBowtie](https://github.com/Jfortin1/crisprBowtie) to perform gRNA spacer sequence
alignment with Bowtie.
* [crisprScore](https://github.com/Jfortin1/crisprScore) to annotate gRNAs with on-target
and off-target scores.
* [crisprDesign](https://github.com/Jfortin1/crisprDesign) to design and manipulate gRNAs
with `GuideSet` objects. 

# Reproducibility

```{r}
sessionInfo()
```



