---
title: "crisprVerse: ecosystem of R packages for CRISPR gRNA design"
output: 
  github_document:
    toc: true
---

```{r, echo=FALSE, results="hide"}
options("knitr.graphics.auto_pdf"=TRUE)
```

Authors: Jean-Philippe Fortin, Luke Hoberecht

Date: July 25, 2022



```{r, show=FALSE, echo=FALSE}
library(BiocStyle)
```

# Installation and getting started

The crisprVerse is a collection of packages for CRISPR guide RNA (gRNA) design
that can easily be installed with the `crisprVerse` package. This provides 
a convenient way of downloading and installing all crisprVerse packages 
with a single R command. 

The package can be installed from the Bioconductor devel branch using
the following commands in an R session:

```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(version="devel")
BiocManager::install("crisprVerse")
```

The core crisprVerse includes the packages that are commonly used for 
gRNA design, and are attached when you attach the `crisprVerse` package:

```{r}
library(crisprVerse)
```


You can check that all crisprVerse packages are up-to-date with 
`crisprVerse_update()`:

```{r}
crisprVerse_update()
```

The complete documentation for the package can be found [here](https://bioconductor.org/packages/devel/bioc/manuals/crisprVerse/man/crisprVerse.pdf).

# Components

The following packages are installed and loaded with the `crisprVerse` package: 

* `r BiocStyle::Biocpkg("crisprBase")` to specify and manipulate CRISPR nucleases.
* `r BiocStyle::Biocpkg("crisprBowtie")` to perform gRNA spacer sequence
alignment with Bowtie.
* `r BiocStyle::Biocpkg("crisprScore")` to annotate gRNAs with on-target
and off-target scores.
* `r BiocStyle::Biocpkg("crisprDesign")` to design and manipulate gRNAs
with `GuideSet` objects. 
* `r BiocStyle::Biocpkg("crisprViz")` to visualize gRNAs.

# Reproducibility

```{r}
sessionInfo()
```



