---
title: "crisprVerse: ecosystem of R packages for CRISPR gRNA design"
author: 
- name: Jean-Philippe Fortin
  affiliation: Data Science and Statistical Computing, gRED, Genentech
  email: fortin946@gmail.com
- name: Luke Hoberecht
  affiliation: Data Science and Statistical Computing, gRED, Genentech
  email: lukehob3@gmail.com
date: "`r Sys.Date()`"
output: 
  BiocStyle::html_document:
    toc_float: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{crisprVerse}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


# Installation and getting started

The crisprVerse is a collection of packages for CRISPR guide RNA (gRNA) design
that can easily be installed with the `crisprVerse` package. This provides 
a convenient way of downloading and installing all crisprVerse packages 
with a single R command. 

The package can be installed from the Bioconductor devel branch using
the following commands in an R session:

```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(version="devel")
BiocManager::install("crisprVerse")
```

The core crisprVerse includes the packages that are commonly used for 
gRNA design, and are attached when you attach the `crisprVerse` package:

```{r}
library(crisprVerse)
```

You can check that all crisprVerse packages are up-to-date 
with the function `crisprVerse_update()`.



# Components

The following packages are installed and loaded with the `crisprVerse` package: 


* `r BiocStyle::Biocpkg("crisprBase")` to specify and manipulate CRISPR nucleases.
* `r BiocStyle::Biocpkg("crisprBowtie")` to perform gRNA spacer sequence
alignment with Bowtie.
* `r BiocStyle::Biocpkg("crisprScore")` to annotate gRNAs with on-target
and off-target scores.
* `r BiocStyle::Biocpkg("crisprDesign")` to design and manipulate gRNAs
with `GuideSet` objects. 

# Reproducibility

```{r}
sessionInfo()
```



